---
title: 'Statistical Inference Course Project, Part 2'
output: html_document
---
Assignment Description

Analyze the ToothGrowth data in the R datasets package.
1.Load the ToothGrowth data and perform some basic exploratory data analyses
2.Provide a basic summary of the data.
3.Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)
4.State your conclusions and the assumptions needed for your conclusions


Load Data

```{r}
library(datasets)

```
Data Analysis
```{r}
library(ggplot2)
ggplot(data=ToothGrowth, aes(x=as.factor(dose), y=len,)) +
geom_bar(stat="identity",) +
  facet_grid(. ~ supp) + 
xlab("Dose in miligrams") + 
ylab("Tooth length") + 
guides(fill=guide_legend(title="Supplement type")) 

```
```{r}
fit <- lm(len ~ dose + supp, data=ToothGrowth)
summary(fit )
confint(fit)
```


Conclusions
1.From the plot, it is clear that as the dose increases, the effectiveness of the both the methods increases.
2.From the hypothesis and confidence interval analysis, for lower dose values (0.5 and 1.0),is an effective method while for higher dose value (2.0), both methods achieve parity.

